\ac{smFRET} is a powerful technique used for studying nanometer-scale dynamics of individual molecules. In solution-based smFRET, it is possible to investigate intra- and intermolecular conformations, binding and unbinding events, and conformational changes under biologically relevant conditions without ensemble averaging. 
However, traditional single-spot smFRET measurements in solution are inherently time-consuming.

In this study, I present a high-throughput smFRET approach that overcomes the limitations of single-spot measurements. This method utilizes a multispot confocal geometry, where excitation spots are optically coupled to two custom silicon \ac{SPAD} arrays. By implementing \ac{PAX}, two-color excitation is achieved, which allows differentiation between singly- and doubly-labeled molecules, in a process called molecular sorting. By pooling data from multiple confocal spots, I demonstrate the ability of this setup to rapidly identify molecular subpopulations and accurately determine their associated FRET efficiencies.

Furthermore, this high-throughput approach enhances the temporal resolution of single-molecule FRET population characterization from minutes to seconds. When combined with microfluidics, this methodology opens doors for real-time kinetic studies and efficient molecular screening applications.

By employing this high-throughput smFRET technique, I aim to advance our understanding of single-molecule dynamics and facilitate a wide range of biophysical investigations in various fields.


%Single-molecule Förster resonance energy transfer (smFRET) is a powerful technique for nanometer-scale studies of single molecules. Solution-based smFRET, in particular, can be used to study equilibrium intra- and intermolecular conformations, binding/unbinding events and conformational changes under biologically relevant conditions without ensemble averaging. However, single-spot smFRET measurements in solution are slow. Here, we detail a high-throughput smFRET approach that extends the traditional single-spot confocal geometry to a multispot one. The excitation spots are optically conjugated to two custom silicon single photon avalanche diode (SPAD) arrays. Two-color excitation is implemented using a periodic acceptor excitation (PAX), allowing distinguishing between singly- and doubly-labeled molecules. We demonstrate the ability of this setup to rapidly and accurately determine FRET efficiencies and population stoichiometries by pooling the data collected independently from the multiple spots. We also show how the high throughput of this approach can be used o increase the temporal resolution of single-molecule FRET population characterization from minutes to seconds. Combined with microfluidics, this high-throughput approach will enable simple real-time kinetic studies as well as powerful molecular screening applications.