\vspace*{\fill}

I am sincerely grateful for the guidance, mentorship, and inspiration provided by my advisor, Dr. Shimon Weiss. 
You been extremely supportive of me, even when it was a challenge to do so. 
You accepted me into your group when I was struggling with my coursework and never once made me feel inferior for my learning disabilities. 
When I had a medical emergency and my daughter was born three months early, 
you allowed me to work from home for an entire year.
I was able to protect her from COVID-19 when she was most at risk, and the time I spent with her was precious beyond measure.
I am truly grateful for your patience and support during my trying entrance to motherhood.
Without it, I would not be so fortunate as to find myself in this position now.
Last, and certainly not least, you respectfully guided me through my academic journey, and for that I am eternally thankful. 

In addition, I would like to thank Dr. Xavier Michalet, for his clever mind and immaculate science.
While I have not always shown my gratitude, your influence has been enormous, and I attribute my hard-won scientific skepticism to you. 
Thank you for so carefully editing my manuscript.
Even though there we difficult moments, working with you was a master course in scientific writing and publishing. 
Thank you for your detailed feedback in group meetings.
Your careful eye inspired me to elevate my presentations to a professional level.
You are a pillar in the Shimon Weiss Lab, and my experience would not have been complete without you.
I will miss our conversations over lunch and your dry sense of humor. 

Thank you Dr. SangYoon Chung for giving me a second chance. 
I know that I am rough around the edges and not always an easy person to like.
In the last few years, our friendship has blossomed, and I cherish it more than you can know. 
You are extremely humble, despite of your breadth of knowledge and expertise in the field of biophysics, which is a truly intersectional study requiring you to be an expert in optics, molecular biology, biochemistry, instrumentation, and data science. 
I thank you for our many conversations and for being so helpful and generous with your time.

Thanks to Dr. Yazin Alhadid.
who trained me in molecular biology and who so patiently waited for me to become interested in the biology side of things. 
May we enjoy many more chats over mint tea and black plums. 

Thank you Dr. Arkaprabha Basu, who has become more family than friend. 
You don't let me get away with anything, and I love you for it.
You and your family have accepted me with open arms, and I am so deeply grateful for your presence in my life.

Thanks to Dr. Eitan Lerner, who spent many hours explaining biophysical phenomena to me. 
Your depth of understanding is impressive, and your willingness to share is unmatched. 
I am not at all surprised to see you flourish in academia.
May you enjoy a long and successful career. 

To Dr. Antonio Ingargiola, your influence has been monumental.
You took me under your wing, and you empowered me with Python.
You taught me all of the ways to utilize technology to my advantage, and in many cases, to surpass my peers who had previously outperformed me in my written coursework. 
You taught me the importance of open science and practical things like version control and rubber duck debugging.
Your influence cannot be underestimated, and I am deeply grateful of our time together. 
I hope to meet you in Italy one day. 

Furthermore, I would like to express my appreciation to my friends and family for their unwavering support, understanding, and encouragement throughout this journey. 
To my husband, Nir - 
it is certainly not easy be married to a scientist that hates to be wrong.
Thank you for your patience, and thank you for giving me the family I have always wanted. 

Finally, I would like to extend my thanks to the funding agencies that have supported my research financially, including grants from the NIH (R01 GM095904, R01 GM069709, R01 GM130942), the NSF awards (MCB 1244175, MCB 1818147, EAGER 1842951), a seed grant from the UCLA Jonsson Comprehensive Cancer Center, and the HFSP award RGP0061/2019. 

\vspace{3em}

\noindent{}I am truly grateful for the collective efforts and contributions of all those who have played a part in my academic and personal growth.

\vspace*{\fill}